%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Sr. Software Engineer} % Job title
{Virtual Diamond Boutique} % Organization
{Gurgaon, India} % Location
{May 2019 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed a small team of developers, that involved hiring, technical planning, code reviews and mentorship}
\item {Worked on multiple design and architectural problems in iOS and iPad }
\item {Build multiple module and frameworks for internal iOS Apps}
\item {Worked on VoIP solutions using Twilio and solved multiple real time data sync usecases using sockets }
\end{cvitems}
}

%------------------------------------------------    

\cventry
{iOS Developer} % Job title
{App Web Studios Technologies Pvt Ltd} % Organization
{Gurgaon, India} % Location
{Apr. 2018 - Apr. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for the design, development, planning modification and/or improvement of applications}
\item {Supervised a team, collaborated closely with back-end, front-end, and QA team}
\item {Developed a Rich Notification feature.}
\item {Worked on Bluetooth APIs.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{iOS Developer} % Job title
{Technokriti Solutions LLP.} % Organization
{Noida, India} % Location
{Jan. 2017 - Mar, 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed feature for run time video processing and watermarking using OpenGL.}
\item {Payment flow and gateway integration}
\item {Build multiple apps for E-Commerce, Food delivery and Social Media sectors }
\end{cvitems} 
}

%------------------------------------------------

\cventry
{iOS Developer} % Job title
{WeddingOnClick} % Organization
{Delhi, India} % Location
{Aug. 2016 - Jan. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Took care of complete app, that involved planning, designing, building and unit testing (XCTest)}
\item {Profiled the application extensively using Instruments to improve performance}
\end{cvitems}
}


%------------------------------------------------

\cventry
{iOS Developer} % Job title
{Freelancing} % Organization
{Gurgaon, India} % Location
{Oct. 2014 - Jul. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created CabX application for a price comparison between various types of online car rental services.}
\item {Created a Student Management system Application to monitor activity and performance.}
\item {Build a third party app for photo gallery using unsplash.com API with image editing options.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{iOS Developer} % Job title
{ColorVill} % Organization
{Chennai, India} % Location
{Jul. 2013 - Sep. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked with Product and UX teams to implement new features and updates}
\item {Developed an E-Commerce app for selling local items }
\end{cvitems}
}

%------------------------------------------------

\end{cventries}